An exploratory analysis of the influence of resource use on the yield verse quality trade-off in Australian vineyards

### 2023-08-01 article.tex
draft conclusion

\subsection{Limitations}
Limitations included overestimating yield for models 1 and 2, and underestimating crop value in models 3 and 4 (see appendix). The issue of model 1 and 2 over predicting yield, may have been due to preventative measures brought on by regional pressures such as fire, frost and disease. Where, more resources were required to prevent these issues from spreading within a region, thus disproportionately effecting some vineyards compared to others locally. This type of maintenance is not well captured especially when considering that some regions, especially those in warmer areas, are not as prone to disease as cooler climates and could potentially have lower operating costs per hectare. This could create a discrepancy in vineyards that utilised preventative measures in wetter regions, as opposed to those that did not, thus expending less fuel and energy but risking disease. When reviewing the differences between regions it is important to consider that vineyards in 'Hot Very Dry' areas can be hundreds of times the size of those in other regions. This limitation could be overcome by incorporating the profitability of vineyards, compare the financial success of working at different operational scales.
\newline
 %The possible reason behind this effect was that different strategies are likely employed between different regions, where some regions target the mass production of cheaper grapes over quality. % ALSO THAT CATASTROPHES HAPPEN EVEN ON SMALL SCALES THis needs to be tied up better.
%Reviewing data to uncover reasons for the disparity between production and quality of similar vineyards  included the use of 
Variables such as the utilisation of renewable energy, contractors, and the occurrence of disease, fire and frost were originally explored to capture the discrepancies between similar vineyards that produced different  yields and crop values. However, none of these variables were significantly connected to the response variables, and did not add to model accuracy; even when considered as interactions. The use of other methods, specifically splines, resulted in more normally distributed residuals but at a drastically reduced overall accuracy when comparing $R^2$ and Residual Square Error. Attempts to fully explain small variations was always overshadowed by the dramatic differences in regional trends.
\newline
Having more data for each region would also be an improvement, allowing greater comparison between regions. More variables may also help to discern vineyards that can produce larger volumes of grapes at higher prices. The use of semi transparent tools such as random forests and decision trees alongside more variables and data may help to uncover the reasons for values that were under or overestimated. These differences could be caused by the use of alternative sustainable practices in the field. And, while there is evidence to suggest that environmentally sustainable practices can reduce costs, increase efficiency, whilst improving the quality of grapes; more research is needed to link these benefits across different regions and climates \citep{baianoOverviewSustainabilityWine2021,marianiSustainableWinegrowingCurrent2015,montalvo-falconSustainabilityResearchWine2023}.
\section{Conclusion}
% This belongs in the discussion

>>>>

\subsection{Limitations}
Limitations included overestimating yield for models 1 and 2, and underestimating crop value in models 3 and 4 (see appendix). The issue of model 1 and 2 over predicting yield, may have been due to preventative measures brought on by regional pressures such as fire, frost and disease. Where, more resources were required to prevent these issues from spreading within a region, thus disproportionately effecting some vineyards compared to others locally. This type of maintenance is not well captured especially when considering that some regions, especially those in warmer areas, are not as prone to disease as cooler climates and could potentially have lower operating costs per hectare. This could create a discrepancy in vineyards that utilised preventative measures in wetter regions, as opposed to those that did not, thus expending less fuel and energy but risking disease. When reviewing the differences between regions it is important to consider that vineyards in 'Hot Very Dry' areas can be hundreds of times the size of those in other regions. This limitation could be overcome by incorporating the profitability of vineyards, compare the financial success of working at different operational scales.
\newline
 %The possible reason behind this effect was that different strategies are likely employed between different regions, where some regions target the mass production of cheaper grapes over quality. % ALSO THAT CATASTROPHES HAPPEN EVEN ON SMALL SCALES THis needs to be tied up better.
%Reviewing data to uncover reasons for the disparity between production and quality of similar vineyards  included the use of 
Variables such as the utilisation of renewable energy, contractors, and the occurrence of disease, fire and frost were originally explored to capture the discrepancies between similar vineyards that produced different  yields and crop values. However, none of these variables were significantly connected to the response variables, and did not add to model accuracy; even when considered as interactions. The use of other methods, specifically splines, resulted in more normally distributed residuals but at a drastically reduced overall accuracy when comparing $R^2$ and Residual Square Error. Attempts to fully explain small variations was always overshadowed by the dramatic differences in regional trends.
\newline
Having more data for each region would also be an improvement, allowing greater comparison between regions. More variables may also help to discern vineyards that can produce larger volumes of grapes at higher prices. The use of semi transparent tools such as random forests and decision trees alongside more variables and data may help to uncover the reasons for values that were under or overestimated. These differences could be caused by the use of alternative sustainable practices in the field. And, while there is evidence to suggest that environmentally sustainable practices can reduce costs, increase efficiency, whilst improving the quality of grapes; more research is needed to link these benefits across different regions and climates \citep{baianoOverviewSustainabilityWine2021,marianiSustainableWinegrowingCurrent2015,montalvo-falconSustainabilityResearchWine2023}.
\section{Conclusion}
% This belongs in the discussion
In summary, vineyard yield and crop value is well-defined by the resources used. However, it is important to consider a vineyard's business goal, region, external pressures and economies of scale. Where, larger vineyards are likely to produce greater overall yields, and have higher yield per area. Smaller vineyards are likely to produce more value per area, and a higher quality of grape. It is likely that regional constraints also contribute to the best strategy to pursue when considering quality or quantity.
%
